---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

whoisxmlapi is an R package to interface with the [WhoisXMLAPI](https://www.whoisxmlapi.com/) service

The package expects the WhoisXMLAPI username and password to be in the `WHOISXMLAPI_USERNAME` and `WHOISXMLAPI_PASSWORD` variables, respectively.

The only functions curently available are retrieving a WHOIS record and looking up account information. If you have access to the other WhoisXMLAPI services please shoot me a note to help collaborate on this package.

The following functions are implemented:

- `account_balance`:	Query the account balance for the account associated with 'WHOISXMLAPI_USERNAME'
- `whois`:	Retrieve WHOIS details for one or more domain names
- `whoisxmlapi_password`:	Get or set WHOISXMLAPI_PASSWORD value
- `whoisxmlapi_username`:	Get or set WHOISXMLAPI_USERNAME value

### News

- Version 0.0.0.9000 released

### Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/whoisxmlapi")
```

```{r echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
options(width=120)
```

### Usage

```{r}
library(whoisxmlapi)

# current verison
packageVersion("whoisxmlapi")

dplyr::glimpse(account_balance())

```

### Test Results

```{r}
library(whoisxmlapi)
library(testthat)

date()

test_dir("tests/")
```

### Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). 
By participating in this project you agree to abide by its terms.
