---
output: rmarkdown::github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "##",
  fig.path = "README-",
  message = FALSE, 
  warning = FALSE,
  fig.retina = 2
)
options(width=120)
```

# whoisxmlapi

Query 'IP' and Domain Information from 'WhoisXMLAPI'

## Description

The 'WhoisXMLAPI' (<https://whoisxmlapi.com/>) service provides
current and historical metadata on 'IP' addresses and 'WHOIS' records 
for internet domain names. Methods are provided to query and process
query results.

## What's Inside the Tin?

The following functions are implemented:

- `account_balance`:	Query the account balance
- `whois`:	Retrieve WHOIS details for one or more domain names
- `whoisxmlapi_key`:	Get or set WHOISXMLAPI_KEY

## Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/whoisxmlapi")
```

## Usage

```{r}
library(whoisxmlapi)

# current verison
packageVersion("whoisxmlapi")

```

```{r}
dplyr::glimpse(account_balance())
```

## `whoisxmlapi` Metrics

```{r cloc, echo=FALSE}
cloc::cloc_pkg_md()
```

### Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.
